---
title: "3. Analyses Plan"
description: |
  Analyze and compare data
author:
  - name: Hauke Roggenkamp 
    url: https://github.com/Howquez
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(magrittr)
library(kableExtra)
library(downloadthis)
```


# Background 

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report is the third in a series of reports covering this project. It reads the data prepared in the previous reports and analyzes them.

```{r readData}
load(file="../data/processed/rda/gaechter2017.rda")        # read gaechter
load(file="../data/processed/rda/gaechter2017_R1.rda")     # read gaechterFirstRound
load(file="../data/processed/rda/replication2021.rda")     # read replication
load(file="../data/processed/rda/replication2021_R1.rda")  # read replicationFirstRound
```

```{r cbind}
main <- rbindlist(list(replication, gaechter), 
                  use.names = TRUE)

R1   <- rbindlist(list(replicationFirstRound, gaechterFirstRound), 
                  use.names = TRUE)
```


